---
title: "FinalProject_NMC245"
author: "Bailey, Cade, ElseLucia, Felix, Libby,"
date: "12/3/2020"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    orientation: rows
    vertical_layout: scroll
    css: style.css
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(prettydoc)

total_trends <- read_csv("total_trends.csv")
total_trends_ID <- read_csv("total_trends_ID.csv")
```

Row {data-height=500}
-------------------------------------
### Correlation between number of likes and verified users vs unverified by Cade Thomas {data-height=650}

```{r verified, echo=FALSE}
ggplot(total_trends, aes(author_verified,stats_diggCount,color=stats_diggCount)) + geom_jitter()+scale_colour_continuous(name = "# of Likes")+labs(title="Verified users and unverified users VS Likes", x="Author", y="Likes")
```

### Explanation {.no-title}
This graph compares the number of likes on the posts of Verified users and Unverified users. As it turns out, there are larger more isolated instances of verified users getting a lot of likes. And for the unverified users they don't have a lot of likes but they do have a very high volume of likes. This shows that unverified users getting lucky on Tik Tok reach more viewers than some of the verified users.

Row {data-height=500}
-------------------------------------

### Will they Actually Like & Share? by ElseLucia Knudsen


```{r,echo=FALSE}

total_trends <- read_csv("total_trends.csv")
  ggplot(total_trends,aes(stats_playCount, stats_diggCount, colour=stats_shareCount))+geom_point()+
  ggtitle("If they see it will they like & share?")+xlab("Views")+ylab("Likes")+scale_colour_continuous(name = "Shares")
```

### Explanation {.no-title}
This graph compares the number of likes on the posts of Verified users and Unverified users. As it turns out, there are larger more isolated instances of verified users getting a lot of likes. And for the unverified users they don't have a lot of likes but they do have a very high volume of likes. This shows that unverified users getting lucky on Tik Tok reach more viewers than some of the verified users.The graphs above show the correlation between how many views a TikTok got with how many likes and shares it also got. In theory, for someone to get the most viral they can is not just about views, the video also needs likes and shares. Using this graph we can analyze if a video with a lot of views also has a lot of likes and shares. If there are outliers in this pattern we would want to look into why that video got popular without the three ingredients that normally are needed to go viral. The first graph shows all of our data points, the graph tells us that there are very few videos that get a high number of Views, Likes, and Shares. The second graph zooms in and excludes those large outliers. This is useful to observe the most common combination of Views, Likes, and Shares. The last graph shows just the outliers. This is helpful because we can study what the best combination is for maximum viral potential.    

Row
-------------------------------------    
### Chart 2 {.no-title}

```{r,echo=FALSE}
total_trends%>%
  filter(stats_playCount<10000000)%>%
  ggplot(aes(stats_playCount, stats_diggCount, colour=stats_shareCount))+geom_point()+
  ggtitle("Will they like & share?","Minus outliers")+xlab("Views")+ylab("Likes")+scale_colour_continuous(name = "Shares")
```
 
### Chart 3 {.no-title}
    
```{r,echo=FALSE}
total_trends%>%
  filter(stats_playCount>10000000)%>%
    ggplot(aes(stats_playCount, stats_diggCount, colour=stats_shareCount))+geom_point()+
  ggtitle("Will they like & share?","Only outliers")+xlab("Views")+ylab("Likes")+scale_colour_continuous(name = "Shares")

```

Row
-------------------------------------

### Correlatino between Video Duration and Video Likes

by Bailey Breving

Row
-------------------------------------
### Video Duration vs. Video Likes {data-padding=10}
```{r duration, echo=FALSE}
ggplot(total_trends, aes(video_duration, authorStats_diggCount, colour=author_verified))+geom_jitter()+xlab("Video Duration")+ylab("Video Likes")+
  ggtitle("Video Duration vs. Video Likes")+theme(plot.title = element_text(hjust = 0.5))+
  scale_colour_discrete(name = "Verified User Status", labels = c("Non-Verified", "Verified"))
```

>There is a trend in video likes declining the longer the TikTok video duration. There is no correlation between user popularity and verified user status. Shorter videos receive more likes than longer videos.

### Video Duration vs. Video Like {data-padding=10}
```{r duration2, echo=FALSE}
total_trends%>%
  filter(authorStats_diggCount < 5000)%>%
  ggplot(aes(video_duration, authorStats_diggCount, colour=author_verified))+geom_jitter()+xlab("Video Duration")+ylab("Video Likes")+
  ggtitle("Video Duration vs. Video Likes")+theme(plot.title = element_text(hjust = 0.5))+
  scale_colour_discrete(name = "Verified User Status", labels = c("Non-Verified", "Verified"))
```

>Taking a closer look: There is a strong correlation between shorter videos ranging between 10-20 seconds that receive the majority of likes. Interestingly enough, the “Verified Users” seem to plateau in their video likes no matter the duration of their TikTok videos. 

Row
-------------------------------------
### Felix

```{r felix, echo=FALSE}
total_trends%>%
  ggplot(aes(video_duration, stats_shareCount, color=authorStats_heart))+geom_jitter()+
  ggtitle("Correlation between video duration and share count by their amount of likes")+xlab("Video duration")+ylab("Share count")+scale_colour_continuous(name = "Likes per video")
total_trends%>%
filter(video_duration<20)%>%
  ggplot(aes(video_duration, stats_shareCount, color=authorStats_heart))+geom_jitter()+
  ggtitle("Correlation between video duration and share count by their amount of likes <20")+xlab("Video duration")+ylab("Share count")+scale_colour_continuous(name = "Likes per video")
total_trends%>%
filter(video_duration>20)%>%
  ggplot(aes(video_duration, stats_shareCount, color=authorStats_heart))+geom_jitter()+
  ggtitle("Correlation between video duration and share count by their amount of likes >20")+xlab("Video duration")+ylab("Share count")+scale_colour_continuous(name = "Likes per video")

```

Row
-------------------------------------
### Username Verification with View, Comments, and Shares 

by Jessica Jucas
Here is a graph that shows the correlation between a Tik Tok creator's username and their video play count. This graph also combines data that shows each video's comment and share count for each of those videos, based on the size and color of each data point. The shape of each plotted point reference if that particular Tik Tok creator is verified or not within the app. This graph shows what you would predict within the Tik Tok community, that the more views a video gets, the more shares and comments it will get as well. Most videos that make it to such a high view count are from verified creators, however, there were a larger number of outliers of unverified users than one would expect.  

```{r, echo=FALSE}
ggplot(total_trends_ID, aes(New_ID, stats_playCount, colour=stats_shareCount, size=stats_commentCount, shape=author_verified))+geom_jitter()+xlab("Creator Nickname")+ylab("Video Play Count")+scale_colour_continuous(name="Share Count")+scale_size_continuous(name="Comment Count")+scale_shape_discrete(name="Author Verification")

```

