---
title: "Correlation between video duration vs. video likes"
date: 8 Dec 2020
Name: Bailey Breving
output: flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(readr)
total_trends <- read_csv("/home/brevingb/Cultural20/unit_three/total_trends.csv")
```
```{r}

ggplot(total_trends, aes(video_duration, authorStats_diggCount, colour=author_verified))+geom_jitter()+xlab("Video Duration")+ylab("Video Likes")+
  ggtitle("Video Duration vs. Video Likes")+theme(plot.title = element_text(hjust = 0.5))+
  scale_colour_discrete(name = "Verified User Status", labels = c("Non-Verified", "Verified"))

```

There is a trend in video likes declining the longer the TikTok video duration. There is no correlation between user popularity and verified user status. Shorter videos receive more likes than longer videos.


```{r cars}
library(dplyr)
library(ggplot2)
total_trends%>%
  filter(authorStats_diggCount < 5000)%>%
  ggplot(aes(video_duration, authorStats_diggCount, colour=author_verified))+geom_jitter()+xlab("Video Duration")+ylab("Video Likes")+
  ggtitle("Video Duration vs. Video Likes")+theme(plot.title = element_text(hjust = 0.5))+
  scale_colour_discrete(name = "Verified User Status", labels = c("Non-Verified", "Verified"))
  
  
```

Taking a closer look: There is a strong correlation between shorter videos ranging between 10-20 seconds that receive the majority of likes. Interestingly enough, the “Verified Users” seem to plateau in their video likes no matter the duration of their TikTok videos. 

