---
title: "Jessica Tik Tok Markdown"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)

total_trends <- read_csv("total_trends.csv")
```

## Username Verification with View, Comments, and Shares 

Here is a graph that shows the correlation between a Tik Tok creators username and their video play count. This graph also combines data that shows each videos comment and share count for each of those videos, based off the size and color of each data point. The shape of each plotted point reference if that particular Tik Tok creator is verified or not within the app. This graph shows what you would predict within the Tik Tok community, that the more views a video gets, the more shares and comments it will get as well. Most videos that make it to such a high view count are from verified creators, however there were a larger number of outliers of unverified users than one would expect. 

```{r cars}
ggplot(total_trends, aes(author_nickname, stats_playCount, colour=stats_shareCount, size=stats_commentCount, shape=author_verified))+geom_jitter()+xlab("Creator Nickname")+ylab("Video Play Count")+scale_colour_continuous(name="Share Count")+scale_size_continuous(name="Comment Count")+scale_shape_discrete(name="Author Verification")

```

